---
title: "Portfolio 1"
---

> The projects should be numbered consecutively (i.e., in the order in which you began them), and should include for each project a description of the goal, the product (computer program, hand graph, computer graph, etc.), the data, and some interpretation. Reports must be reproducible and of high quality in terms of writing, grammar, presentation, etc.

```{r load-packages, warning = FALSE, message=FALSE}
library(tidyverse) 
library(tidyr)
library(scales)

```
```{r}
library(readr)

nc_winston_salem_2020_04_01 <- read_csv("nc_winston-salem_2020_04_01.csv")

```

The data in this set contains crime numbers and statistics from Winston-Salem between the years 2000 and 2015.

The goal of this portfolio piece is to create plots that will visualize data contrasting the gender and race in regards to the amount of searches conducted. Although in this portfolio, I will not be able to make a judgment about whether discrimination exists 

I found this dataset using Stanford's open policing database and selected it because of it's topicality to Wake Forest.

```{r glimpse at the crime statistics}
glimpse(nc_winston_salem_2020_04_01)
```
```{r create new variable for searches only}
wsnc_search <- nc_winston_salem_2020_04_01 %>%
  filter(search_conducted == TRUE)
```
```{r create a binary white or not white category}
wsnc_search <- wsnc_search %>%
  mutate(not_white = subject_race != "white")
```
```{r}
nc_winston_salem_2020_04_01 <- nc_winston_salem_2020_04_01 %>%
  mutate(not_white = subject_race != "white")
```
```{r}
nc_winston_salem_2020_04_01 <- nc_winston_salem_2020_04_01 %>%
  mutate(searched = isTRUE(search_conducted))
```




Right now, I am only interested in police records where searches are made. I want to see if there is a difference in searches made between sex and race. Thus, I created a new variable that filters filters the dataset down to police activity where searches are conducted. I also created a new value that states whether the subject is white or not white. This will help me when I want to plot race.


```{r}
ggplot(wsnc_search, aes(x = subject_sex)) +
  geom_bar() +
  labs(
    title = "Searches by Gender",
    x = "Gender",
    y = "Number of Searches"
  )
```
```{r}
ggplot(wsnc_search, aes(x = not_white)) +
  geom_bar() +
  labs(
    title = "Searches by race",
    x = "Non-White",
    y = "Number of Searches")
```
Here I've shown in bar graph form the difference in number of non-white searches vs. white searches and male searches vs. female searches as well as a faceted  My goal here is to find whether there is apparent gender discrimination or racial discrimination in frequency of search and then visualize this information. This would also require me to account for the proportion of total violations based on white or not white and female or male.

```{r}
ggplot(wsnc_search, aes(x=subject_sex)) + geom_bar() + facet_wrap(~not_white)+
  labs(
    title="Searches by Gender and Race (False=White, True=Not White)",
    x = "Gender",
    y=" Number of Searches"
  )
```


```{r}
table(wsnc_search$not_white)
```
```{r}
table(nc_winston_salem_2020_04_01$not_white)
```
```{r}
(3197/199175)*100
```
This number is the percent of white people who were searched. I divided the total amount of searched white people by the total amount of white people who were stopped by police. Below I do the same thing for non white people.
```{r}
(6012/253385)*100
```
```{r}
table(wsnc_search$subject_sex)
```
```{r}
table(nc_winston_salem_2020_04_01$subject_sex)
```
```{r}
(1630/184701)*100
```
```{r}
(7579/267859)*100
```

In the next portfolio piece, it is my goal to be able to plot in a faceted bar plot, the number of searches proportionate to the amount of people in each category. This will help visualize the real difference between gender and race. 
