---
title: "Portfolio 2"
---

I'm back. Right now I am going to attempt to visualize the data we worked with in the last portfolio piece but now it will hopefully be proportioned such that it's a proportion of the total population of that category in the data. Ex: searched men / total men * 100 = true percentage of searched men

```{r}
table(wsnc_search$not_white)
```
```{r}
table(nc_winston_salem_2020_04_01$not_white)

```

```{r}
(3197/199175)*100
not_white_total<-df3[2]

not_white_searched<-df4[2]


```
This number is the percent of white people who were searched. I divided the total amount of searched white people by the total amount of white people who were stopped by police. Below I do the same thing for non white people.
```{r}
(6012/253385)*100

df3<-table(nc_winston_salem_2020_04_01$not_white)

white_total<-df3[1]

df4<-table(wsnc_search$not_white)

white_searched<-df4[1]
```

```{r}
table(wsnc_search$subject_sex)
```
```{r}
table(nc_winston_salem_2020_04_01$subject_sex)
```

```{r}
(1630/184701)*100

df<-table(nc_winston_salem_2020_04_01$subject_sex)

men_total <- df[2]


df2<-table(wsnc_search$subject_sex)

men_searched<- df2[2]
```

```{r}
(7579/267859)*100

df<-table(nc_winston_salem_2020_04_01$subject_sex)

women_total <- df[1]

df2<-table(wsnc_search$subject_sex)

women_searched<- df2[1]
```
I've now created 8 new values (really 12 including the dataframes) that will help me in the calculation and visualization of the true data.

```{r}
white_percentage_searched <- (white_searched / white_total) * 100
not_white_percentage_searched <- (not_white_searched/ not_white_total) * 100

men_percentage_searched <- (men_searched / men_total) * 100
women_percentage_searched <- (women_searched / women_total) * 100
```

```{r}
```



