---
title: "Portfolio 5"
---

The data set I am using has a list of all the edible plants known in the world. 

```{r}
library(tidyverse)
library(dplyr)
```


```{r}
library(tidytuesdayR)
```
```{r}
tt_datasets(2026)
```
```{r}
plants<-tt_load("2026-02-03")
```

```{r}
plantsp5 <- plants$edible_plants

glimpse(plantsp5)
```
I am going to be visualizing different relationships between different variables. In this portfolio, I will create three visualizations between different variables. Those relationships will be sunlight and water (to test if more sunlight needed=more water needed), temperature germination and days germination and soil and water to see if there is a correlation between different types of soil and water necessity. 

```{r}
plantsp5$water
```

First, I'll visualize the sunlight and water levels, but to do this, I am going to categorize the levels of water needed in numbers increasing by amount 1- 

```{r}
plantsp5 <- plantsp5 %>%
  mutate(
    waternumber = case_when(
      water == "Very High" ~ "5 (Very High)",
      water == "very high" ~ "5 (Very High)",

      water == "High" ~ "4 (High)",
      water == "high" ~ "4 (High)",

      water == "Medium" ~ "3 (Medium)",
      water == "medium" ~ "3 (Medium)",

      water == "Low" ~ "2 (Low)",
      water == "low" ~ "2 (Low)",

      water == "Very Low" ~ "1 (Very Low)",
      water == "Very low" ~ "1 (Very Low)"
    )
  )
```
```{r}
plantsp5$waternumber
```
```{r}
plantsp5 <- plantsp5 %>%
  mutate(sunlight=tolower(sunlight))
```
```{r}
plantsp5 <- plantsp5 %>%
  mutate(
    sunlight = recode(
      sunlight,
      "full sun/partial shade/full shade" = "full sun/partial shade/ full shade"))
```

```{r}
plantsp5 %>%
  ggplot(aes(x = sunlight, fill = factor(waternumber))) +
  geom_bar(position = "stack") +
  labs(
    x = "Sunlight Required",
    y = "Count",
    fill = "Water Level"
  )
```
This tells us a lot about each category. The data doesn't look very convinceing that there is a correlation between overall sunlight requirement and water requirement. I do however think this data isn't exactly the best at categorizing it's data. I had to do a lot of work above to combine/even out categories and I think that there should be a more numerical way of categorizing some of the sunlight/water level statistics. This would make it much easier to analyze (min rainfall per year required, min sunny days per year required etc.)

Next I will visualize temperature germination and days germination

```{r}
plantsp5 %>%
  ggplot(aes(x=days_germination, y=temperature_germination)) + 
  geom_point() + geom_smooth(method="lm") +
  labs(
    x= "	Optimal germination temperature (Celsius)",
    y= "Days to germination at optimum temperature",
    title = "Germination time (days) by optimal germination temperature"
  )
```




What I've learned from visualizing this data visualizaiton is that this dataset kinda sucks. You can see both along the y and x axis that there are some data points that are ranges and some that are whole numbers. What would help a lot is if we just had whole numbers. Perhaps if this dataset's variable was minimum_temp instead of temperature, we might be able to visualize a result in a way that shows some sort of correlation. There are also some that are n/a or not available which eliminates data from analysis. 

I was hoping to find some sort of correlation (positive or negative) between temperature and days, such that I could plot the dots and ad a line over the data but because the data had ranges and some didn't even apply, it was hard to discern that. 

